\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/conclusion.tex
grammarlized done

Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The scripting mode largely extends the
original BadUSB and successfully bypasses existing defenses. The privacy
extraction mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The remote control mode
archives complete hijack of the target device, allowing us to perform various
type of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further tests its ability under different mode and proves it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtains and analyzes video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

As future work, we will further explore the potential of \textit{isolated UI
rendering} and implement it on a customized operating system. Moreover we also
hope to lower the power consumption for network transmission in \tool to make
it more practical.

>>>>

Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The scripting mode largely extends the
original BadUSB and successfully bypasses existing defenses. The privacy
extraction mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The remote control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different mode and proves it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

As future work, we will further explore the potential of \textit{isolated UI
rendering} and implement it on a customized operating system. Moreover, we also
hope to lower the power consumption for network transmission in \tool to make
it more practical.
